# Course Info {#info}

(ref:email) [paternnj@plu.edu](mailto:paternnj@plu.edu)

**Instructor:** Nick Paterno

**Email:** (ref:email)

### Office Hours

```{r echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
#adjust office hours each semester
library(tidyverse)
Day <- c("Monday", "Tuesday", "Thursday")
Hours <- c("8:00 am - 2:30 pm", rep("1:00 pm - 3:00 pm",2))
df <- data.frame(Day, Hours)
knitr::kable(df) 
```
[Sign Up Here](https://npaterno.youcanbook.me/)

*Campus:* Morken 261 

*Virtual:* via Zoom or Google Meet. 

### Class Schedule
```{r echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
library(tidyverse)
Day <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
Activity <- c("New video lessons posted/Discussion & Problems Session", "Office Hours", "Discussion & Problems Session", "Office Hours", "Live Coding & Workshop")
df <- data.frame(Day, Activity)
knitr::kable(df) 
```

It is assumed that you will have done some reading and/or watched the video lessons **BEFORE** coming to class on Monday and Wednesday. Those classes will start with a brief discussion of the material and segue into a problem solving session.

For the Live Coding \& Workshop sessions, we will start with a lesson on a specific element of statistical computing. This will be the live coding part; you'll have your laptop closed and can watch the process of structuring a file, troubleshooting errors and anything else that can come up when writing code. The remainder of class will be spent in workshop mode, which allows you to begin the lab assignment as well as collaborate with your peers. 

### Class Materials

**Textbook:** [OpenIntro Statistics, 4th Ed](https://leanpub.com/openintro-statistics)

#### Technology:

* Access to a word processing program. 
* [R](https://cran.r-project.org/) and [RStudio](https://rstudio.com/) (These are free and we will get them setup during our first lab day)
* A graphing calculator, preferably a TI-83 or TI-84. A Casio FX-9750GII will also work (useful but *optional*).

## Graded Items and Grading Guidelines

### Weights of Grades:
```{r echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
library(tidyverse)
Category<- c("Quizzes", "Labs", "Paper", "Final", "Total")
Weight <- c("30%", "25%", "15%", "30%", "100%")
df <- data.frame(Category, Weight)
knitr::kable(df) 
```

#### Homework:
Homework will not be graded but quiz and final exam questions will be heavily based on problems assigned for homework. Solutions to even numbered problems are available upon request. 

#### Quizzes:
There will be one in-class quiz for each chapter (seven total). Quiz questions will be a mix of computation and short answer, no multiple choice. Your lowest quiz score will be dropped.

#### Labs:
We will have weekly coding sessions and workshops with the exception of weeks seven and fourteen. Your lowest two labs (workshop assignments) will be dropped. Late lab submissions will be accepted within 24 hours of the due date with a 15% deduction and will not be accepted past the 24 hour mark. 

#### Paper:
Each student will be required to write a paper about statistics in the media. Details will be given out in the second week of class via email and the Announcements page. The paper is due no later than the Last Day of Instruction (see Important Dates below). If there is a week where you don't have much work in your other classes or our class didn't take you long then you may want to knock out the paper early in the semester.

#### Final:
The final will have two parts: one in-class exam (similar to the quizzes) and a take-home lab to be completed as an RMarkdown file. The lab is due when you come in for the in-class final. Late lab submissions will be accepted within 24 hours of the due date with a 15% deduction and will not be accepted past the 24 hour mark. 

### Important Dates
```{r eval = FALSE, include = FALSE}
#Adjust dates each semester
```

Date  | Event
------------- | -------------
4/2/2021  | No Class: Good Friday
5/21/2021 | Last Day of Instruction
5/24/2021-5/28/2021 | Finals Week
